
---
title: "Comprehensive Marketing & Sales Analysis"
author: "Kalyani Lonkar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This report performs an extensive analysis on marketing, sales and economic data across various regions. It includes preprocessing, exploratory data analysis, time series forecasting, PCA, and multiple regression models.

# Libraries
```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyr)
library(reshape2)
library(caret)
library(glmnet)
library(MASS)
library(car)
library(lmtest)
library(forecast)
library(ggfortify)
library(e1071)
library(corrplot)
```

# Load Data
```{r load-data}
load("CourseWorkData.RData")
head(data)
```

# Data Cleaning and Feature Engineering
```{r feature-engineering}
colnames(data) <- c("Sales","Price","Ad1","Ad2","No_of_stores","Wage","Time","Product","Region","Month","Year")
data$Date <- as.Date(paste(data$Year, data$Month, "1", sep = "-"), format = "%Y-%b-%d")
data$Quarter <- as.numeric(format(data$Date, "%m")) %/% 4 + 1
data$Season <- factor(ifelse(data$Quarter==1,"Winter", ifelse(data$Quarter==2,"Spring", ifelse(data$Quarter==3,"Summer","Autumn"))))

# Feature engineering
data <- data %>%
  mutate(Ad1_sq = Ad1^2, Ad2_sq = Ad2^2, Ad1_Ad2 = Ad1*Ad2, Ad2_Prom = Ad2*No_of_stores,
         Log_Ad1 = log(Ad1+1), Log_Ad2 = log(Ad2+1), Log_Prom = log(No_of_stores+1), 
         Log_Sales = log(Sales+1), Ad1_zero_indicator = ifelse(Ad1==0,1,0))
```

# Correlation Matrix
```{r correlation-matrix}
numerical_columns <- names(data)[sapply(data, is.numeric)]
corr_matrix <- cor(data[,numerical_columns], use="complete.obs")
corrplot(corr_matrix, method="color", type="upper")
```

# PCA
```{r pca-analysis}
scaled_data <- scale(data[,numerical_columns])
pca_result <- prcomp(scaled_data, center=TRUE, scale.=TRUE)
summary(pca_result)
plot(pca_result, type="l")
```

# Regression Example (Mexico)
```{r regression-mexico}
Mexico_data <- data %>% filter(Region == "Mexico")
train_index <- 1:floor(0.8 * nrow(Mexico_data))
train <- Mexico_data[train_index, ]
test <- Mexico_data[-train_index, ]
model <- lm(Log_Sales ~ Log_Ad1 + Ad2 + Wage + Log_Prom + Quarter, data=train)
summary(model)
pred <- predict(model, newdata=test)
rmse <- sqrt(mean((test$Log_Sales - pred)^2))
rmse
```

# Forecast Example (ARIMA)
```{r arima-example}
library(forecast)
sales_ts <- ts(Mexico_data$Sales, frequency=12)
train_ts <- window(sales_ts, end=c(4,12))
fit <- auto.arima(train_ts)
forecast_values <- forecast(fit, h=12)
autoplot(forecast_values)
```

# Conclusion
This report completed a comprehensive analysis involving PCA, regression and time series forecasting. The same workflow can be applied for Singapore, UK, Spain and USA datasets by filtering on `Region`.

